DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems with PDEs

### 2012-12-04 Paper_May_2012/main.tex
Some more modifications to the paper.

>>>>

To obtain thickness values that are either $1$ or $0$, so that we can
interpreter the results in terms of material or no material, we apply the 
so called SIMP-model (Solid Isotropic Material with Penalization) 
with parameter $p = 4$ 
to obtain the distribution given in Fig.~\ref{res:mbb-top}.

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth, viewport=205 88 975 500, clip]{Pictures/MBB-top.png}
\caption{Thickness distribution for the MBB-beam minimum compliance topology optimization problem.} 
\label{res:mbb-top}
\end{figure}
